Introduction to Causal Inference Models

### 2017-08-01 msm_introduction.Rmd
updated msm

To make things easier, let's load some functions I've made for g-computation and IPTW.

>>>>

```{r iptw td}
MSModelR::iptw

# define propensity models (intercept only model without covariates)
pr_a0_mod <- glm(A0 ~ 1, data = td_sim_data, family="binomial")
# probability of being treated at time 1
pr_a0 <- mean(predict(pr_a0_mod, type = "response"))
# pr a1 | stuff

```
To make things easier, let's load some functions I've made for g-computation and IPTW.
